Viscous Transport in Eroding Porous Media

### 2019-09-05 docs/transport/erosion_transport.tex
modify the caption of Figure 16 in transport paper

Finally, using network models for flow in porous media~\cite{}, the
anomalous dispersion rate can be linked to channel widths between solid
bodies.  We construct a Delaunay triangulation with the centers of the
eroding bodies corresponding to the vertices of the triangles.  Then, if
the side of a triangle connects two vertices, we call the bodies
neighbors.  Then, for each pair of neighbors, we measure the distance
between the bodies.  Once a Delaunay triangulation is formed, it is used
for all subsequent time steps until a body completely disappears.  At
this point, a new Delaunay triangulation is formed. 
{\color{red}In Figure~\ref{fig:Eroding100gap_mean_var}, 
we record the gap distances between bodies neighbors and
calculate the mean and variance with respect to porosities. 
For the mean of gap distances, it is linearly increacing until $\phi = 85\%$ 
which means the eroding . 
For the variance of gap distances, it is almost a constant function until $\phi= 85\%$  }
\begin{figure}[H]
\begin{subfigure}[b]{0.5\textwidth}
\includegraphics*[height = 0.8\linewidth]{./figs/gap_mean}
\caption{}
\end{subfigure}
\begin{subfigure}[b]{0.5\textwidth}
\includegraphics*[height=0.8\linewidth]{./figs/gap_variance}
\caption{}
\end{subfigure}
\caption{\label{fig:Eroding100gap_mean_var} (a): The mean of gaps with respect to porosity $\phi$.  
(b): The variance of gaps with respect to porosity $\phi$.}
\end{figure}

>>>>

Finally, using network models for flow in porous media~\cite{}, the
anomalous dispersion rate can be linked to channel widths between solid
bodies.  We construct a Delaunay triangulation with the centers of the
eroding bodies corresponding to the vertices of the triangles.  Then, if
the side of a triangle connects two vertices, we call the bodies
neighbors.  Then, for each pair of neighbors, we measure the distance
between the bodies.  Once a Delaunay triangulation is formed, it is used
for all subsequent time steps until a body completely disappears.  At
this point, a new Delaunay triangulation is formed. 
{\color{red}In Figure~\ref{fig:Eroding100gap_mean_var}, 
we record the gap distances between bodies neighbors and
calculate the mean and variance with respect to porosities. 
For the mean of gap distances, it is linearly increacing until $\phi = 85\%$ 
which means the eroding . 
For the variance of gap distances, it is almost a constant function until $\phi= 85\%$  }
\begin{figure}[H]
\begin{subfigure}[b]{0.5\textwidth}
\includegraphics*[height = 0.8\linewidth]{./figs/gap_mean}
\caption{}
\end{subfigure}
\begin{subfigure}[b]{0.5\textwidth}
\includegraphics*[height=0.8\linewidth]{./figs/gap_variance}
\caption{}
\end{subfigure}
\caption{\label{fig:Eroding100gap_mean_var}  The mean of gaps in (a) and 
the variancewith of gaps in (b) with respect to porosity $\phi$. 
Red stars are six selected porosities to have the details of  
the disturbutions of gaps and fitting curves of the disturbutions 
in Figure~\ref{fig:Eroding100gap_hist}.}
\end{figure}
